Statistical Guarantees for Local Spectral Clustering on Random Neighborhood Graphs

### 2021-09-10 jmlr/revision/ppr_clustering_neighborhood_graph.tex
Newest version of jmlr tex and bib files.

\begin{figure}[tb]
	\centering
	\includegraphics[width=0.495\textwidth]{../lower_bound_1}
	\includegraphics[width=0.495\textwidth]{../lower_bound_2}
	\caption{\it\small The density $f$ in \eqref{eqn:lb_density}, for
		$\rho=1$, and two different choices of $\epsilon$ and $\sigma$. Left:
		$\epsilon = 0.3$ and $\sigma = 0.1$; right: $\epsilon = 0.2$ and 
		$\sigma = 0.2$.} 
	\label{fig:hard_case}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.24\textwidth,scale = .5]{../row1_true_density_cluster}
	\includegraphics[width=0.24\textwidth]{../row1_ppr_cluster}
	\includegraphics[width=0.24\textwidth]{../row1_conductance_cluster}
	\includegraphics[width=0.24\textwidth]{../row1_density_cluster}
	\includegraphics[width=0.24\textwidth]{../row2_true_density_cluster}
	\includegraphics[width=0.24\textwidth]{../row2_ppr_cluster}
	\includegraphics[width=0.24\textwidth]{../row2_conductance_cluster}
	\includegraphics[width=0.24\textwidth]{../row2_density_cluster}
	\includegraphics[width=0.24\textwidth]{../row3_true_density_cluster}
	\includegraphics[width=0.24\textwidth]{../row3_ppr_cluster}
	\includegraphics[width=0.24\textwidth]{../row3_conductance_cluster}
	\includegraphics[width=0.24\textwidth]{../row3_density_cluster}
	\caption{\it\small True density (column 1), PPR (column 2), minimum normalized
		cut (column 3) and estimated density (column 4) clusters for 3 different 
		simulated data sets. Seed node for PPR denoted by a black cross.} 
	\label{fig:moons}
\end{figure}

>>>>

\begin{figure}[tb]
	\centering
	\includegraphics[width=0.495\textwidth]{plots/lower_bound/lower_bound_1}
	\includegraphics[width=0.495\textwidth]{plots/lower_bound/lower_bound_2}
	\caption{\it\small The density $f$ in \eqref{eqn:lb_density}, for
		$\rho=1$, and two different choices of $\epsilon$ and $\sigma$. Left:
		$\epsilon = 0.3$ and $\sigma = 0.1$; right: $\epsilon = 0.2$ and 
		$\sigma = 0.2$.} 
	\label{fig:hard_case}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.24\textwidth,scale = .5]{plots/experiment_2/row1_true_density_cluster}
	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row1_ppr_cluster}
	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row1_conductance_cluster}
	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row1_density_cluster}
	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row2_true_density_cluster}
	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row2_ppr_cluster}
	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row2_conductance_cluster}
	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row2_density_cluster}
	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row3_true_density_cluster}
	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row3_ppr_cluster}
	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row3_conductance_cluster}
	\includegraphics[width=0.24\textwidth]{plots/experiment_2/row3_density_cluster}
	\caption{\it\small True density (column 1), PPR (column 2), minimum normalized
		cut (column 3) and estimated density (column 4) clusters for 3 different 
		simulated data sets. Seed node for PPR denoted by a black cross.} 
	\label{fig:moons}
\end{figure}
